Operational adoption of new probabilistic point rainfall forecasts: the crucial role of user-centric training

### 2020-12-01 manuscript/main.tex

@@

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/ProbFC_Knowledge_Effectiveness_Observed.png}}
\caption{Like Fig.\ref{UND_EFF_estimated}, but it includes the results of the experiment with IMN and OMSZ. Such results show that the gap in the UND-EFF relationship between ecPoint and traditional ensemble-based forecasts is greater than it was estimated at the beginning of the experiment as centres with different ensemble-based forecasts understanding levels performed similarly.}
\label{UND_EFF_observed}
\end{figure}

>>>>

\begin{figure*}
\centerline{\includegraphics[width=39pc]{manuscript/Figures/FlowChart.png}}
\caption{Timeline of the trial phases. The first phase, the "real-time phase", took place between 2018 and 2019 and lasted 12 months. Th second phase, the "offline phase", took place between 2019 and 2021 and lasted 15 months.}
\label{FlowChart}
\end{figure*}

@@

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/ProbFC_Knowledge_Effectiveness_Observed.png}}
\caption{Like Fig.\ref{UND_EFF_estimated}, but it includes the results of the experiment with IMN and OMSZ. Such results show that the real gap in the UND-EFF relationship between ecPoint and traditional ensemble-based forecasts (dashed fuchsia area) is greater than it was estimated at the beginning of the experiment as users with different ensemble-based forecasts understanding levels performed similarly in terms of effective use of such forecasts in decision-making processes.}
\label{UND_EFF_observed}
\end{figure}
